Measurement Clusterization in D-optimal Designs for Bayesian Linear Inverse Problems over Hilbert Spaces

### 2023-05-10 latex/intro.tex
Clusterization illustration with my code

\begin{figure}
  \begin{tikzpicture}[thick, scale=1.3, every node/.style={scale=0.99}]
    \begin{axis}
      %% title={Posterior Pointwise Standard Deviations and D-Optimal
      %% Measurement Locations}
      [xmin = 0, xmax = 3.14, xlabel = {$x \in \Omega$}, ylabel =
        posterior pointwise std, ymin = 0,
      %compat = 1.3,
      % ymax   = 130,
      % ytick = \empty,
      legend cell align=left,
      % legend style={at={(0.45,0.2)}}
      legend pos= outer north east 
      ]
      % \draw[black!30!white, thin] (50,0) -- (50,130);
      % 
      %% \addplot [thin, black, mark=none] table{stdv-heat-sens1-var1.txt};
      %% \addlegendentry{1 measurements};

      %% \addplot [thin, blue, mark=none] table{stdv-heat-sens2-var1.txt};
      %% \addlegendentry{2 measurements};

      %% \addplot [thin, red, mark=none] table{stdv-heat-sens3-var1.txt};
      %% \addlegendentry{3 measurements};

      \addplot [thin, green, mark=none] table{stdv-heat-sens4-var1.txt};
      \addlegendentry{4 measurements};

      \addplot [thin, purple, mark=none] table{stdv-heat-sens5-var1.txt};
      \addlegendentry{5 measurements};

      \addplot [thin, cyan, mark=none] table{stdv-heat-sens6-var1.txt};
      \addlegendentry{6 measurements};

      %% \addplot [black,  only marks, mark=x, mark size=1.5] 
      %% table{locs-heat-sens1-var1.txt}; 
      %% \addplot [blue,   only marks, mark=x, mark size=1.5]
      %% table{locs-heat-sens2-var1.txt}; 
      %% \addplot [red,    only marks, mark=x, mark size=1.5]
      %% table{locs-heat-sens3-var1.txt};
      \addplot [green,  only marks, mark=*, mark size=1.5] 
      table{locs-heat-sens4-var1.txt}; 
      \addplot [purple, only marks, mark=*, mark size=1.5] 
      table{locs-heat-sens5-var1.txt}; 
      \addplot [cyan,   only marks, mark=*, mark size=1.5] 
      table{locs-heat-sens6-var1.txt};

    \end{axis}
  \end{tikzpicture}
  \caption{Measurement clusterization for the inverse problem of
    inferring the initial condition of the 1D heat equation. Posterior
    pointwise standard deviations (lines) are plotted over the
    computational domain $\Omega = [0, \pi]$, for varying numbers of
    measurements. Measurement locations (circles) were chosen
    according to the D-optimality criterion. Measurement
    clusterization occurs for six measurements: Only four measurement
    locations are visible, since two pairs of measurements are so
    close together they are indistinguishable.}
  \label{fig:clusterization illustration}
\end{figure}

@@

%% \subsection{An Example of Measurement Clusterization}\label{subsec:example}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[height=0.5\textwidth]{example.eps}
    \caption{Measurement clusterization for the inversion of the
      initial condition of the 1D heat equation. For each measurement,
      its index is plotted where the measurement is taken. Fmong fou
      locations are plotted over the computational domain $\Omega =
      [0, 1]$ (x-axis), for varying numbers of measurements
      (y-axis). Measurement locations (numbers) were chosen according
      to the D-optimality criterion. Measurement clusterization
      already occurs for four measurements: the third measurement is
      overlaid with the fourth. For five measurements, first and
      second measurements are clustered, as well as the fourth and the
      fifth.}
  \label{fig:clusterization illustration}
\end{figure}

@@
